---
title: "Batch Compliance"
author: Christopher Barrie, Justin Ho, Chung-hong Chan
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Intro. to academictwitteR}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

## Introduction

It is crucial for Twitter data holders to ensure the data reflects user intent and the current state of content on Twitter. Specifically, if a tweet is deleted or modified on Twitter, data holders must delete or modify any content stored offline accordingly. The batch compliance endpoints and corresponding functions offer researchers an easy way to help maintain Twitter data in compliance with the [Twitter Developer Agreement and Policy](https://developer.twitter.com/en/developer-terms/policy).

## Upload Dataset

To create a compliance job and upload a dataset, you can use the `create_compliance_job()` function:

```{r, eval = FALSE}
create_compliance_job(x = "tweet_ids.txt",
                      type = "tweets")
```

You can either supply a vector of tweet/user ids or a text file in which each line contains a Tweet ID or user ID. The contents of the text file can look something like this:
```
1233905174730682369
1233905174659256320
1233905174650986497
1233905174655139841
1233905174663458816
1233905174835449856
1233905174789443584
1233905174533545987
1233905174936080384
```

A sample can be found [here](https://raw.githubusercontent.com/echen102/COVID-19-TweetIDs/master/2020-03/coronavirus-tweet-id-2020-03-01-00.txt).

The function will return a Job ID, which will be used to download the results.

## Check Job Status

Optionally, you can check your job status by running:
```{r, eval = FALSE}
list_compliance_jobs()
```

## Download Results
When a job is completed, you can download the compliance results using:
```{r, eval = FALSE}
get_compliance_result(id = "1460077048991555585")
```

The function will automatically check if the job has completed.

If you forgot your job id, you can retrieve it using `list_compliance_jobs()`.

